Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-05-07 compact_boson.tex
[draft] 1.add bibs, 2. geneneral formulation, free boson lattice done 3. Appendix of winding mode not done yet, I will add the caveat later

\todo[inline]{Remember to mention in the main text, winding sectors have no contribution}
In this appendix, we address the issue of winding modes of compact bosons. Up to now we have exclusively worked with the oscillator modes of free bosons. 
%We have introduced the general formulation of bosonic conformal interface in Sec.~\ref{sec_sub:general_formulation}, and calculated various partition functions from the boundary state approach in App.~\ref{app:gnd_dn_lambda}-\ref{app:lambda_12}. We have not talk about the winding mode for compact bosons. 
Here, we shall show that winding modes for compactified bosons will have no contribution to the fidelity or Loschmidt echo, at least in the leading order. Therefore, the result presented in the main text are ready applied to the case where two compactified bosons of different radii are connected by a conformal interface. \todo[inline]{say intuition why not matter, mention application to Laughlin, etc.}

@@

We consider the following boson configuration
\begin{eqnarray}\begin{aligned}
\phi(x+L,t)=\phi(x,t)+2\pi mR
\end{aligned}\end{eqnarray}
where $m\in\mathbb{Z}$ is the winding number of the field. Since the field is compactified on a circle, its momentum $\pi_0$ takes discrete eigenvalues $\pi_0\equiv\frac{n}{R}$ with $n\in\mathbb{Z}$. Thus the mode expansion reads
\begin{eqnarray}\begin{aligned}
\label{eq:mode_expand_compact}
\phi(x,t)&=\phi_0-\frac{2\pi Rm}{L}x+\frac{\pi_0}{gL}t+\frac{i}{\sqrt{4\pi g}}\sum_{n\neq0}\frac{1}{n}(a_ne^{2\pi i n(x-t)/L}+\bar{a}_{n}e^{2\pi i n(x+t)/L})\\ 
&={\phi}_0-\frac{2\pi Rm}{L}x+\frac{n}{gRL}t+\frac{i}{\sqrt{4\pi g}}\sum_{n\neq0}\frac{1}{n}(a_ne^{2\pi i n(x-t)/L}+\bar{a}_{n}e^{2\pi i n(x+t)/L})
\end{aligned}\end{eqnarray}
Further, the holomorphic coordinates are introduced as
\begin{eqnarray}\begin{aligned}
z=\exp\left(2\pi i\frac{t-x}{L}\right)\qquad\bar{z}=\exp\left(2\pi i\frac{t+x}{L}\right)
\end{aligned}\end{eqnarray}
which leads to 
\todo[inline]{Take care of the format for long equation later, for two columns}
\begin{eqnarray}\begin{aligned}
\label{eq:phi_in_z}
\phi(z,\bar{z})=\phi_0-i\left(\frac{n}{4\pi gR}+\frac{mR}{2}\right)\ln z-i\left(\frac{n}{4\pi gR}-\frac{mR}{2}\right)\ln \bar{z}+\frac{i}{\sqrt{4\pi g}}\sum_{n\neq0}\frac{1}{n}(a_nz^{n}+\bar{a}_{n}\bar{z}^{-n})
\end{aligned}\end{eqnarray}
The key observation is that if one defines
\begin{eqnarray}\begin{aligned}
a_0=\sqrt{4\pi g}\left(\frac{n}{4\pi gR}+\frac{mR}{2}\right)\qquad\bar{a}_0=\sqrt{4\pi g}\left(\frac{n}{4\pi gR}-\frac{mR}{2}\right)\frac{mR}{2}
\end{aligned}\end{eqnarray}
then the holomorphic and anti-holomorphic derivatives can be written compactly as
\begin{eqnarray}\begin{aligned}
i\partial\phi(z)=\frac{1}{\sqrt{4\pi g}}\sum_{n\in\mathbb{Z}}a_{n}z^{-n-1}\qquad i\bar{\partial}\phi(\bar{z})=\frac{1}{\sqrt{4\pi g}}\sum_{n\in\mathbb{Z}}\bar{a}_{n}\bar{z}^{-n-1}
\end{aligned}\end{eqnarray}
\todo[inline]{I will think about how to say this part}
{\bf\color{red}
The Virasoro generators takes the same form as before
\begin{eqnarray}\begin{aligned}
L_n=\frac{1}{2}\sum_{m\in\mathbb{Z}}:a_{n-m}a_m:\qquad n\in\mathbb{Z}
\end{aligned}\end{eqnarray}
In particular for the conformal boundary state $|B\rangle$, the condition
\begin{eqnarray}\begin{aligned}
(L_n-\bar{L}_{-n})|B\rangle=0
\end{aligned}\end{eqnarray}
reduces to 
\begin{eqnarray}\begin{aligned}
\label{eq:DN_a}
\text{Dirichlet}&:a_0-\bar{a}_0=0\rightarrow m=0 \\
\text{Neumann}&:a_0+\bar{a}_0=0\rightarrow n=0
\end{aligned}\end{eqnarray}
}

The conformal boundary state for Dirichlet and Neumann are respectively
\begin{eqnarray}\begin{aligned}
\label{eq:DN_state}
|{\rm D} \rangle  &= g_{\,\!_\text{D}}  \prod_{n > 0 } \exp(\frac{1}{k} a_k^{\dagger} \bar{a}_{-k}^{\dagger} )| \phi_0 \rangle \quad | \phi_0 \rangle = \sum_{n \in \mathbb{Z}} e^{-i \frac{n}{R}\phi_0 } | n, m = 0 \rangle \\
| {\rm N} \rangle &= g_{\,\!_\text{N}} \prod_{n > 0 } \exp(\frac{1}{k} a_k^{\dagger} \bar{a}_{-k}^{\dagger} )| \bar{\phi}_0 \rangle \quad | \bar{\phi}_0 \rangle = \sum_{n \in \mathbb{Z}} e^{i m \bar{\phi}_0 } | n = 0, m \rangle 
\end{aligned}\end{eqnarray}
with the desired boundary conditions
\begin{eqnarray}\begin{aligned}
\phi(x,t=0)|{\rm D} \rangle=\phi_0|{\rm D} \rangle\qquad \partial_t \phi( x, t = 0 ) | {\rm N } \rangle = 0
\end{aligned}\end{eqnarray}

\subsection{Winding mode with Gluing Condition}
\label{app_sub:compact_gluing_boundary}
We recall that the conformal boundary condition can be written as
\begin{eqnarray}\begin{aligned}
\label{eq:def_S_in_app}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S(\theta)
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix}
\end{aligned}\end{eqnarray}
where the scattering matrices are given in Eq.~\eqref{eq:S1_S2}. We shall specialize to the case $S=S_1$ first. The folding sends $\phi^2(x)\rightarrow\phi^2(-x)$ for $x<0$, and the $\partial_x\phi^2$ term changes sign, we therefore have 
\begin{eqnarray}\begin{aligned}
\label{eq:def_S_in_app_2}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_+\phi^2
\end{pmatrix}
=S_1(\theta)
\begin{pmatrix}
\partial_-\phi^1\\
\partial_-\phi^2
\end{pmatrix}
\end{aligned}\end{eqnarray}
Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:phi_in_z}, we have
\todo[inline]{Check this one}
\begin{eqnarray}\begin{aligned}
\label{eq:def_S_in_app_2}
\sum_{n\in\mathbb{Z}}\begin{pmatrix}
\bar{a}_n^1\bar{z}^{-n}\\
\bar{a}_n^2\bar{z}^{-n}
\end{pmatrix}
=S_1(\theta)
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
a_n^1{z}^{-n}\\
a_n^2{z}^{-n}
\end{pmatrix}
\end{aligned}\end{eqnarray}
{\bf\color{red}The boundary condition is imposed at $t=0$, where $\bar{z}=z^{-1}$}, therefore we have
\begin{eqnarray}\begin{aligned}
a^i_n-(S^{-1}_{ij})\bar{a}^j_{-n}=0
\end{aligned}\end{eqnarray}
This is clearly a generalization of Dirichlet and Neumann boundary conditions in Eq.~\eqref{eq:DN_a}. We therefore expect that the conformal boundary state is a generalization of Eq.~\eqref{eq:DN_state}, subject to the more general constraint 
\todo[inline]{check this one in the note}
\begin{eqnarray}\begin{aligned}
\label{eq:S_1_constraint}
\tan\theta=\frac{n_2R_1}{n_1R_2}=-\frac{m_1R_1}{m_2R_2}
\end{aligned}\end{eqnarray}
Thus we conclude that the conformal boundary state reads
\begin{eqnarray}\begin{aligned}
g_{S_1}\sum_{S_1}e^{in_1\phi_0-im_1\bar{\phi}_0}|n_1,m_1\rangle|n_2,m_2\rangle
\end{aligned}\end{eqnarray}
where $\sum_{S_1}$ is the summation consistent with the constraint in Eq.~\eqref{eq:S_1_constraint}. The g-factor can only be determined by Cardy condition\cite{oshikawa_boundary_2010}. Since it is not important for what follows, we shall not repeat the calculation here. For the case of $S=S_2$, it is evident that the same calculation can be carried out, and one will arrive at the similar boundary state.

\subsection{Winding Mode Contribution to the Partition Function}
\label{app_sub:winding_contribution}
We are ready to demonstrate that the winding mode will have no contribution to the leading order of $\beta$. We shall reconsider the partition function as shown in Fig.~\ref{fig:fig_lambda_1_lambda_2}
\begin{eqnarray}\begin{aligned}
Z=\langle\lambda_2|e^{-\pi H}|\lambda_1\rangle\qquad H=\frac{2\pi}{\beta}(L_0+\bar{L}_0)
\end{aligned}\end{eqnarray}
For the winding mode contribution, we simply replace $L_0$($\bar{L}_0$) with $a_0$($\bar{a}_0$). For the case of same boundary state $\lambda_1=\lambda_2$, we have the winding mode contribution as
\begin{eqnarray}\begin{aligned}
\label{eq:Z0}
Z_0 = \sum_{S_1 } g_{\,\!_{\lambda_1} }g_{\,\!_{\lambda_2} } \exp\Big\{- \frac{4\pi}{\beta} 2 \pi g ( \frac{n_1}{ 4 \pi R_1 g} + \frac{m_1 R_1 }{ 2} )^2 \Big\}
\end{aligned}\end{eqnarray}
In the $\beta\rightarrow\infty$ limit, Eq.~\eqref{eq:Z0} can be approximated by a simple two dimensional integral
\begin{eqnarray}\begin{aligned}
Z_0\approx g_{\,\!_{\lambda_1} }g_{\,\!_{\lambda_2} } (\sqrt{\beta})^2\int dxdy\exp\Big\{-8 \pi^2 g ( \frac{x}{ 4 \pi R_1 g} + \frac{y R_1 }{ 2} )^2 \Big\}\propto\beta
\end{aligned}\end{eqnarray}
Thus the winding mode will contribute at most a $\ln\beta$ term to the free energy. Compared to the result in App.~\ref{app:gnd_dn_lambda}-\ref{app:lambda_12}, we conclude that the winding mode contribution is negligible in the large $\beta$ limit.

For the case $\lambda_1=\lambda_2$, the partition function will acquire non-zero contribution from the least common divisor of $(n_1,m_1)$ and $(n_2,m_2)$. The same conclusion still holds in the limit $\beta\rightarrow\infty$.

>>>>

\todo[inline]{Remember to mention in the main text, winding sectors have no contribution}
In this appendix, we address the issue of winding modes of compact bosons. In the main text, we have exclusively worked with the oscillator modes of free bosons. 
%We have introduced the general formulation of bosonic conformal interface in Sec.~\ref{sec_sub:general_formulation}, and calculated various partition functions from the boundary state approach in App.~\ref{app:gnd_dn_lambda}-\ref{app:lambda_12}. We have not talk about the winding mode for compact bosons. 
Here, we shall show that winding modes for compactified bosons will have no contribution to the fidelity or Loschmidt echo, at least in the leading order. Therefore, our results are ready to be applied in the case where two compactified bosons of different radii are connected by a conformal interface\cite{PhysRevLett.118.136801}. \todo[inline]{say intuition why not matter, mention application to Laughlin, etc.}

@@

We consider the following boson configuration
\begin{eqnarray}\begin{aligned}
\phi(x+L,t)=\phi(x,t)+2\pi mR
\end{aligned}\end{eqnarray}
where $m\in\mathbb{Z}$ is the winding number of the field. Since the field is compactified on a circle, its momentum $\pi_0$ takes discrete eigenvalues $\pi_0\equiv\frac{n}{R}$ with $n\in\mathbb{Z}$. Thus the mode expansion reads
\begin{eqnarray}\begin{aligned}
\label{eq:mode_expand_compact}
\phi(x,t)&=\phi_0-\frac{2\pi Rm}{L}x+\frac{\pi_0}{gL}t+\frac{i}{\sqrt{4\pi g}}\sum_{n\neq0}\frac{1}{n}(a_ne^{2\pi i n(x-t)/L}+\bar{a}_{n}e^{2\pi i n(x+t)/L})\\ 
&={\phi}_0-\frac{2\pi Rm}{L}x+\frac{n}{gRL}t+\frac{i}{\sqrt{4\pi g}}\sum_{n\neq0}\frac{1}{n}(a_ne^{2\pi i n(x-t)/L}+\bar{a}_{n}e^{2\pi i n(x+t)/L})
\end{aligned}\end{eqnarray}
Further, the holomorphic coordinates are introduced as
\begin{eqnarray}\begin{aligned}
z=\exp\left(2\pi i\frac{t-x}{L}\right)\qquad\bar{z}=\exp\left(2\pi i\frac{t+x}{L}\right)
\end{aligned}\end{eqnarray}
which leads to 
\todo[inline]{Take care of the format for long equation later, for two columns}
\begin{eqnarray}\begin{aligned}
\label{eq:phi_in_z}
\phi(z,\bar{z})=\phi_0-i\left(\frac{n}{4\pi gR}+\frac{mR}{2}\right)\ln z-i\left(\frac{n}{4\pi gR}-\frac{mR}{2}\right)\ln \bar{z}+\frac{i}{\sqrt{4\pi g}}\sum_{n\neq0}\frac{1}{n}(a_nz^{n}+\bar{a}_{n}\bar{z}^{-n})
\end{aligned}\end{eqnarray}
The key observation is that if one defines
\begin{eqnarray}\begin{aligned}
a_0=\sqrt{4\pi g}\left(\frac{n}{4\pi gR}+\frac{mR}{2}\right)\qquad\bar{a}_0=\sqrt{4\pi g}\left(\frac{n}{4\pi gR}-\frac{mR}{2}\right)
\end{aligned}\end{eqnarray}
then the holomorphic and anti-holomorphic derivatives can be written compactly as
\begin{eqnarray}\begin{aligned}
i\partial\phi(z)=\frac{1}{\sqrt{4\pi g}}\sum_{n\in\mathbb{Z}}a_{n}z^{-n-1}\qquad i\bar{\partial}\phi(\bar{z})=\frac{1}{\sqrt{4\pi g}}\sum_{n\in\mathbb{Z}}\bar{a}_{n}\bar{z}^{-n-1}
\end{aligned}\end{eqnarray}
%The Virasoro generators takes the same form as before
%\begin{eqnarray}\begin{aligned}
%L_n=\frac{1}{2}\sum_{m\in\mathbb{Z}}:a_{n-m}a_m:\qquad n\in\mathbb{Z}
%\end{aligned}\end{eqnarray}
%In particular for the conformal boundary state $|B\rangle$, the condition
%\begin{eqnarray}\begin{aligned}
%(L_n-\bar{L}_{-n})|B\rangle=0
%\end{aligned}\end{eqnarray}

$a_0$ and $\bar{a}_0$ are not independent for the conformal boundary states. It turns out that from the Virasoro generators, one can deduce that
\begin{eqnarray}\begin{aligned}
\label{eq:DN_a}
\text{Dirichlet}&:a_0-\bar{a}_0=0\\
\text{Neumann}&:a_0+\bar{a}_0=0
\end{aligned}\end{eqnarray}
Therefore, the conformal boundary state for Dirichlet and Neumann are respectively
\begin{eqnarray}\begin{aligned}
\label{eq:DN_state}
|{\rm D} \rangle  &= g_{\,\!_\text{D}}  \prod_{k > 0 } \exp(\frac{1}{k} a_k^{\dagger} \bar{a}_{-k}^{\dagger} )| \phi_0 \rangle \quad | \phi_0 \rangle = \sum_{n \in \mathbb{Z}} e^{-i \frac{n}{R}\phi_0 } | n, m = 0 \rangle \\
| {\rm N} \rangle &= g_{\,\!_\text{N}} \prod_{k > 0 } \exp(\frac{1}{k} a_k^{\dagger} \bar{a}_{-k}^{\dagger} )| \bar{\phi}_0 \rangle \quad | \bar{\phi}_0 \rangle = \sum_{n \in \mathbb{Z}} e^{i m \bar{\phi}_0 } | n = 0, m \rangle 
\end{aligned}\end{eqnarray}
with the desired boundary conditions
\begin{eqnarray}\begin{aligned}
\phi(x,t=0)|{\rm D} \rangle=\phi_0|{\rm D} \rangle\qquad \partial_t \phi( x, t = 0 ) | {\rm N } \rangle = 0
\end{aligned}\end{eqnarray}
We have included the oscillator part in Eq.~\eqref{eq:DN_state}, with the vacuum being a linear combination of different winding sectors. In the following sections, the oscillator part will be the same, and we shall write down only the vacuum which is subject to the more general gluing condition.

\subsection{Winding mode with Gluing Condition}
\label{app_sub:compact_gluing_boundary}

\todo[inline]{Say the caveat, where is the bounadry}

We recall that the conformal boundary condition can be written as
\begin{eqnarray}\begin{aligned}
\label{eq:def_S_in_app}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S(\theta)
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix}
\end{aligned}\end{eqnarray}
where the scattering matrices are given in Eq.~\eqref{eq:S1_S2}. We shall specialize to the case $S=S_1$ first. The folding sends $\phi^2(x)\rightarrow\phi^2(-x)$ for $x<0$, and the $\partial_x\phi^2$ term changes sign, we therefore have 
\begin{eqnarray}\begin{aligned}
\label{eq:def_S_in_app_2}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_+\phi^2
\end{pmatrix}
=S_1(\theta)
\begin{pmatrix}
\partial_-\phi^1\\
\partial_-\phi^2
\end{pmatrix}
\end{aligned}\end{eqnarray}
Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:phi_in_z}, we have
\begin{eqnarray}\begin{aligned}
\label{eq:def_S_in_app_2}
\sum_{n\in\mathbb{Z}}\begin{pmatrix}
\bar{a}_n^1\bar{z}^{-n}\\
\bar{a}_n^2\bar{z}^{-n}
\end{pmatrix}
=S_1(\theta)
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
a_n^1{z}^{-n}\\
a_n^2{z}^{-n}
\end{pmatrix}
\end{aligned}\end{eqnarray}
As explained above, the boundary condition is imposed at $t=0$, where $\bar{z}=z^{-1}$, therefore we have
\begin{eqnarray}\begin{aligned}
a^i_n-(S^{-1}_{ij})\bar{a}^j_{-n}=0
\end{aligned}\end{eqnarray}
This is clearly a generalization of Dirichlet and Neumann boundary conditions in Eq.~\eqref{eq:DN_a}. We therefore expect that the conformal boundary state is a generalization of Eq.~\eqref{eq:DN_state}, subject to the more general constraint 
\begin{eqnarray}\begin{aligned}
\label{eq:S_1_constraint}
\tan\theta=\frac{n_2R_1}{n_1R_2}=-\frac{m_1R_1}{m_2R_2}
\end{aligned}\end{eqnarray}
Thus we conclude that the conformal boundary state reads
\begin{eqnarray}\begin{aligned}
g_{S_1}\sum_{S_1}e^{in_1\phi_0-im_1\bar{\phi}_0}|n_1,m_1\rangle|n_2,m_2\rangle
\end{aligned}\end{eqnarray}
where $\sum_{S_1}$ is the summation consistent with the constraint in Eq.~\eqref{eq:S_1_constraint}. The g-factor can only be determined by Cardy condition\cite{oshikawa_boundary_2010}. Since it is not important for what follows, we shall not repeat the calculation here. For the case of $S=S_2$, it is evident that the same calculation can be carried out, and one will arrive at the similar boundary state.

\subsection{Winding Mode Contribution to the Partition Function}
\label{app_sub:winding_contribution}
In order to demonstrate that the winding mode will have no contribution to the leading order of $\beta$, we shall reconsider the partition function as shown in Fig.~\ref{fig:fig_lambda_1_lambda_2}
\begin{eqnarray}\begin{aligned}
Z=\langle\lambda_2|e^{-\pi H}|\lambda_1\rangle\qquad H=\frac{2\pi}{\beta}(L_0+\bar{L}_0)
\end{aligned}\end{eqnarray}
For the winding mode contribution, we simply replace $L_0$($\bar{L}_0$) with $a_0$($\bar{a}_0$). For the case of same boundary state $\lambda_1=\lambda_2$, we have the winding mode contribution as
\begin{eqnarray}\begin{aligned}
\label{eq:Z0}
Z_0 = \sum_{S_1 } g_{\,\!_{\lambda_1} }g_{\,\!_{\lambda_2} } \exp\Big\{- \frac{4\pi}{\beta} 2 \pi g ( \frac{n_1}{ 4 \pi R_1 g} + \frac{m_1 R_1 }{ 2} )^2 \Big\}
\end{aligned}\end{eqnarray}
In the limit $\beta\rightarrow\infty$, Eq.~\eqref{eq:Z0} can be approximated by a simple two dimensional integral
\begin{eqnarray}\begin{aligned}
Z_0\approx g_{\,\!_{\lambda_1} }g_{\,\!_{\lambda_2} } (\sqrt{\beta})^2\int dxdy\exp\Big\{-8 \pi^2 g ( \frac{x}{ 4 \pi R_1 g} + \frac{y R_1 }{ 2} )^2 \Big\}\propto\beta
\end{aligned}\end{eqnarray}
Thus the winding mode will contribute at most a $\ln\beta$ term to the free energy. Compared to the result in App.~\ref{app:gnd_dn_lambda}-\ref{app:lambda_12}, we conclude that the winding mode contribution is negligible in the large $\beta$ limit.

For the case $\lambda_1\neq\lambda_2$, the partition function will acquire non-zero contribution from the least common divisor of $(n_1,m_1)$ and $(n_2,m_2)$. The same conclusion still holds in the limit $\beta\rightarrow\infty$.

### 2017-05-07 free_boson_lattice.tex
[draft] 1. general formulation & App. F almost done. Pass 2. Next I will do free boson lattice and fidelity definition
[draft] 1.add bibs, 2. geneneral formulation, free boson lattice done 3. Appendix of winding mode not done yet, I will add the caveat later

{\bf\color{red} Say motivation: in low energy go to CFT}

{\bf\color{red} Say goal: Demonstrate the S matrix is conformal invariance}

>>>>

In this section, we consider a lattice model with bosonic defect at the center, which reduces to the one considered in Sec.~\ref{sec_sub:general_formulation} in the continuum limit\cite{calabrese_entanglement_2012}. Therefore, it serves as a numerical tool to check our analytic results in Sec.~\ref{sec:analytic_numerics}. Despite its simpleness, such discrete bosonic defect can be considered in more general quadratic bosonic\cite{PhysRevA.74.022329}, or fermionic\cite{PhysRevB.64.064412} systems. It also sheds light on the possible application of our CFT results in condensed matter experiments\cite{Rohringer2015,Trotzky2012}.

\todo[inline]{Remove the citations if not relevant...}

We imagine connecting two coupled harmonic chains, which consists in total $2n$ coupled harmonic oscillators labeled by $\left\{\phi_{-n+1},...,\phi_0,\phi_1,...,\phi_n\right\}$. There is a bond defect between site $0$ and $1$, and the Hamiltonian reads
\begin{eqnarray}\begin{aligned}
H = \frac{1}{2} \sum_i \pi_i^2  +  \frac{1}{2} \sum_{i\ne 0 }  ( \phi_i - \phi_{i+1} )^2  +  \frac{1}{2} \begin{pmatrix}  \phi_0, \phi_1 \end{pmatrix}
\begin{bmatrix}
1 + \Sigma_{11}  & \Sigma_{12} \\
\Sigma_{21} &  1 + \Sigma_{22} \\
\end{bmatrix}
\begin{pmatrix}
\phi_0 \\
\phi_1 
\end{pmatrix}
\end{aligned}\end{eqnarray}
where $\pi_i$ is the conjugate momentum. Later we shall see the matrix $\Sigma_{ij}$ is related to the scattering matrix in Sec.~\ref{sec_sub:general_formulation}, and thus characterizes all possible bosonic defects discussed there.

It is straightforward to write down the ansatz for this quantum mechanical problem, (the use of $(n-1)$ in $\phi_n^B$ simplifies the calculation)
\begin{equation}
\label{eq:ansatz}
\phi_n
= \left\lbrace
  \begin{aligned}
    \phi_n^A &= A_{-} e^{i \omega t  - inka}  + A_{+} e^{i \omega t  + inka}  & \quad  n \le 0 \\
    \phi_n^B &= B_{-} e^{i \omega t  - i(n-1)ka}  + B_{+} e^{i \omega t  + i(n-1)ka} & \quad n \ge 1 \\
  \end{aligned} \right. 
 \quad 
\end{equation}
where $a$ is the lattice constant. The dispersion of the system reads
\begin{eqnarray}\begin{aligned}
\label{eq:dispersion}
\omega=\left|2\sin\frac{k}{2}\right|
\end{aligned}\end{eqnarray}
which implies the system is gapless. The defect will not break the criticality of the harmonic chain\cite{peschel_exact_2012}. Upon plugging Eq.~\eqref{eq:ansatz}-\eqref{eq:dispersion} into the equation of motion, we have the following relation between the incoming and outgoing amplitudes
\begin{equation}
\label{eq:discrete_S}
\begin{bmatrix}
\Sigma_{11} + e^{-ik} & \Sigma_{12} \\
\Sigma_{21} & \Sigma_{22}  + e^{-ik}  \\
\end{bmatrix}
\begin{pmatrix}
A_{-} \\
B_{+}\\
\end{pmatrix}
=-
\begin{bmatrix}
\Sigma_{11} +e^{ik} & \Sigma_{12}\\
\Sigma_{21} & \Sigma_{22} + e^{ik}
\end{bmatrix}
\begin{pmatrix}
A_{+}\\
B_{-}\\
\end{pmatrix}
\end{equation}
and the scattering matrix can be solved as
\begin{equation}
  S = \frac{-1}{ \det \Sigma  + e^{-ik} \text{tr} \Sigma   + e^{-2ik}}
\begin{bmatrix}
\det \Sigma+ \Sigma_{11} e^{-ik} + \Sigma_{22} e^{ik}+1  & -2i \sin k \Sigma_{12}  \\
-2i \sin k \Sigma_{21} &  \det \Sigma+ \Sigma_{11} e^{ik} + \Sigma_{22} e^{-ik}+1\\
\end{bmatrix}
\end{equation}
It is clear that Eq.~\eqref{eq:discrete_S} is a discrete analogue of Eq.~\eqref{eq:def_S}, with momentum dependence. The necessary condition for the scattering matrix to be scale invariance is that the ratio $|S_{11}/S_{21}|$ is independent of $k$. This implies 
\begin{equation}
\label{eq:Sigma_condition}
\det \Sigma = -1, \, \, \text{tr} \Sigma = 0
\end{equation}
Therefore, we have the scale invariant S-matrix as
\begin{equation}
S = \frac{1}{1 - e^{-2ika } } ( -2i \sin k ) \Sigma
 = - e^{ika} \Sigma
\end{equation}
In the continuum limit where $a\rightarrow0$, the matrix $\Sigma$ can be parameterized as
\begin{equation}
\Sigma = -\lim_{a \rightarrow 0 } S = 
\begin{bmatrix}
\frac{\lambda^2- 1}{1 + \lambda^2} & \frac{-2\lambda }{1 + \lambda^2} \\
\frac{-2\lambda }{1 + \lambda^2} & \frac{1- \lambda^2}{1 + \lambda^2} \\
\end{bmatrix}
\end{equation}
in accordance to Eq.~\eqref{eq:Sigma_condition}.

{\bf\color{red}
Say in the continuum limit, what happens

say in the long time, what happens?

say the special case in the boundary
}

This is the matrix we will use for the numerics. The results will be presented in Sec.~\ref{sec:analytic_numerics}.
